ggalluvial: Layered Grammar for Alluvial Plots

### 2021-04-11 README.rmd
pkg(readme): describe vignettes & credit uf health - fixes #61

The documentation contains several examples; use `help()` to call forth examples of any layer (`stat_*` or `geom_*`) or of the conversion functions (`to_*_form`).

@@

Development of this package benefitted from the use of equipment and the support of colleagues at [UConn Health](https://health.uconn.edu/).

>>>>

Several additional vignettes offer detailed solutions to specific needs:

* "Labeling small strata" (`"labels"`) for how to elegantly label strata of a wide range of heights in an alluvial plot;
* "The Order of the Rectangles" (`"order-rectangles"`) for how to control the positioning of strata and lodes in an alluvial plot; and
* "Tooltips for ggalluvial plots in Shiny apps" (`"shiny"`) for how to incorporate alluvial plots into interactive apps.

The object documentation includes several more examples. Use `help()` to call forth more detail on

* any layer (`stat_*` or `geom_*`),
* the conversion functions (`to_*_form`), and
* the data sets installed with the package (`vaccinations` and `majors`).

@@

Development of this package benefitted from the use of equipment and the support of colleagues at [UConn Health](https://health.uconn.edu/) and at [UF Health](https://ufhealth.org/).
